---
title: "ACS County Targets"
author: Casey Breen
---

Summary: This notebook contains code to construct reference data for multilevel with post-stratification (MRP). We use the 5-year 2018 ACS to create our post-stratification targets. 


## Library function + helper code

```{r}
## library here package
library(here)

## Load helper functions and library all packages used for analysis
source(here("code", "models", "mrp", "helpers.R"))
```


## Load data 

Read in 5-yr ACS with IPUMSR package

```{r}
## read in ipums data
acs18_5yr <- read_ipums_micro(ddi = here("data", "ACS", "acs_5yr2018", "usa_00032.xml"), verbose = F)

## fips code
fips <- readRDS(here("data", "mrp", "input", "fips.rds"))
```

## Format data 

Recode the ACS variables to match BICS variables. Drop variables we won't use. 

```{r}
## Recode and prep variables
acs18_5yr_recode <- acs18_5yr %>%
  ## filter(AGE >= 18) %>%
  janitor::clean_names() %>%
  mutate(
    educ = case_when(
      educ %in% 0:5 ~ "Non-high school graduate",
      educ == 6 ~ "High school graduate",
      educ %in% 7:9 ~ "Some college",
      educ %in% 10:11 ~ "College graduate"
    ),
    race = case_when(
      raced == 100 & hispan == 0 ~ "White",
      raced == 200 & hispan == 0 ~ "Black",
      raced > 200 & hispan == 0 ~ "Other",
      hispan > 0 ~ "Hispanic"
    ),
    hhsize = case_when(
      numprec == 1 ~ "1",
      numprec == 2 ~ "2",
      numprec == 3 ~ "3",
      numprec == 4 ~ "4",
      numprec == 5 ~ "5",
      numprec >= 6 ~ "6+"
    ),
    gender = case_when(
      sex == 1 ~ "Male",
      sex == 2 ~ "Female"
    ),
    agecat = cut(age,
      # breaks = c(18, 25, 35, 45, 65, 100),
      breaks = c(0, 18, 25, 35, 45, 55, 65, 100),
      include.lowest = TRUE,
      right = FALSE
    ),
    countyfip = str_pad(countyfip,
      width = 3,
      side = "left",
      pad = "0"
    ),
    state_fips = str_pad(statefip,
      width = 2,
      side = "left",
      pad = "0"
    ),
    county_fips = paste0(state_fips, countyfip)
  ) %>%
  left_join(fips, by = c("state_fips" = "state_code")) %>%
  select(educ, race, hhsize, gender, agecat, county_fips, state, perwt) %>%
  janitor::clean_names()
```

## Create post-stratification targets

```{r}
## state targets for post-stratification
acs_state_reference <- acs18_5yr_recode %>%
  group_by(state, agecat, gender, hhsize, race) %>%
  summarize(count = sum(perwt)) %>%
  ungroup() %>%
  group_by(agecat, state) %>%
  mutate(prop = count / sum(count)) %>%
  ungroup()

## state targets for symmetry
acs_state_symmetry <- acs18_5yr_recode %>%
  group_by(state, agecat) %>%
  summarize(count = sum(perwt)) %>%
  ungroup() %>%
  group_by(state) %>%
  mutate(prop = count / sum(count)) %>%
  ungroup()

## national targets for symmetry
acs_national_symmetry <- acs18_5yr_recode %>%
  group_by(agecat) %>%
  summarize(count = sum(perwt)) %>%
  ungroup() %>%
  mutate(prop = count / sum(count)) %>%
  ungroup()
```

## Write out targets

```{r}
## state level targets
write_rds(acs_state_reference, here("data", "mrp", "input", "acs_state_reference.rds"))

## state level symmetry
write_rds(acs_state_symmetry, here("data", "mrp", "input", "acs_state_symmetry.rds"))

## national level symmetry
write_rds(acs_national_symmetry, here("data", "mrp", "input", "acs_national_symmetry.rds"))
```
