---
title: "Google PCA"
author: Casey Breen
---

## Summary 

This script takes raw mobility mobility reports from Google (https://www.google.com/covid19/mobility/) creates a rolling 3 week averagr of the first principal component of the 7 measures. Specifically, 

— Read in Google mobility reports data 
— Perform multiple imputation to simulate missing values (missing bc of privacy concerns)
— Calculate principal component decomposition
— Calculate 3-week rolling average for each day X state combination 

## Library function + helper code  

```{r}
## library here package
library(here)

## Load helper functions and library all packages used for analysis
source(here("code", "helpers.R"))
```


## Read in data 

```{r, message = FALSE}
## read raw google mobility data
google_mobility_data_2020 <- read_csv(here("data", "input", "2020_US_Region_Mobility_Report.csv"), col_types = cols())
google_mobility_data_2021 <- read_csv(here("data", "input", "2021_US_Region_Mobility_Report.csv"), col_types = cols())

google_mobility_data <- bind_rows(google_mobility_data_2020, google_mobility_data_2021)

## date first accessed (restrict to cases before Jul)
google_mobility_data_state <- google_mobility_data %>%
  filter(!is.na(sub_region_1) & is.na(sub_region_2)) %>%
  filter(date <= as_date("2021-06-28")) %>%
  rename(
    google_grocery = grocery_and_pharmacy_percent_change_from_baseline,
    google_parks = parks_percent_change_from_baseline,
    google_transit = transit_stations_percent_change_from_baseline,
    google_workplaces = workplaces_percent_change_from_baseline,
    google_residential = residential_percent_change_from_baseline,
    google_retail = retail_and_recreation_percent_change_from_baseline
  ) %>%
  select(
    state = sub_region_1,
    date,
    starts_with("google")
  )
```


## Impute missing values 

```{r}
## Some missing data for (1) parks and (2) transit
google_mobility_data_state %>%
  select(starts_with("google")) %>%
  summarise_all(~(sum(is.na(.))))

## impute values using mice package
tempData <- suppressWarnings(mice(data = google_mobility_data_state, m = 1, maxit = 50, meth = "pmm", seed = 500, print = F))

google_mobility_data_state_imputed <- complete(tempData, 1)
```


## Principal Component Decomposition

```{r}
## select mobility indicators
pca_data <- google_mobility_data_state_imputed %>%
  select(google_grocery, google_parks, google_transit, google_workplaces, google_residential, google_retail)

## principal components
res.pca <- prcomp(pca_data, scale = TRUE)

## take
individual_pca <- as.data.frame(res.pca$x)

## add pca back onto code
google_mobility_data_pca <- google_mobility_data_state_imputed %>%
  bind_cols(individual_pca)

## calculate 3 week rolling average of pc1
google_mobility_data_pca <- google_mobility_data_pca %>%
  group_by(state) %>%
  mutate(rolling_pca_3wks = zoo::rollmean(x = PC1, 21, fill = NA, align = "center"))
```


## Format and save mobility data 

```{r}
## switch to state abbreviations
google_mobility_data_pca <- google_mobility_data_pca %>%
  mutate(estimated_state = state.abb[match(state, state.name)]) %>%
  mutate(state = case_when(
    state == "District of Columbia" ~ "DC",
    TRUE ~ estimated_state
  ))


## write out pca file
write_rds(google_mobility_data_pca, file = here("data", "intermediate", "google_mobility_pca.rds"))
```
