---
title: "Non Pharmaceutical Interventions (Oxford)"
output: html_notebook
---

## Summary 

This script takes raw mobility mobility reports from Google (https://www.google.com/covid19/mobility/) creates a rolling 3 week averagr of the first principal component of the 7 measures. Specifically, 

— Read in Google mobility reports data 
— Perform multiple imputation to simulate missing values (missing bc of privacy concerns)
— Calculate principal component decomposition
— Calculate 3-week rolling average for each day X state combination 

## Library function + helper code  

```{r}
## library here package
library(here)

## Load helper functions and library all packages used for analysis
source(here("code", "helpers.R"))
```



```{r}
## prepared for model  
df_formodel <- read_rds(here('data', 'input', 'bics_data_waves_1-6.rds')) 


npi_2020 <- read_csv(here("data/input/OxCGRT_withnotes_2020.csv")) %>% 
  janitor::clean_names() %>% 
  filter(country_name == "United States") %>% 
  # select(date, region_name, government_response_index) %>% 
  # filter(region_name != "") %>% 
  mutate(date = lubridate::ymd(date))

npi_2021 <- read_csv(here("data/input/OxCGRT_withnotes_2021.csv")) %>% 
  janitor::clean_names() %>% 
  filter(country_name == "United States") %>% 
  # select(date, region_name, government_response_index) %>% 
  # filter(region_name != "") %>% 
  mutate(date = lubridate::ymd(date))
  
npi <- bind_rows(npi_2020, npi_2021) %>% 
  mutate(state = state.abb[match(region_name, state.name)])

df_formodel <- df_formodel %>% 
  left_join(npi, by = c("state", "date")) 


write_rds(df_formodel, here('data', 'input', 'bics_data_waves_1-6.rds')) 


```

