---
title: "Predict and Post-Stratify"
---

Summary: This notebook contains code to produce post-stratified estimates of social contact and calculate summary statistics for social contact.  

Specifically, this code will: 

1. Predict contact patterns using predictived posterior draws from Bayesian models  
2. Poststratify the predictions
3. Adjust matrices for symmetry
4. Estimate contact for youngest age group (not surveyed)
5. Calculate contact matrices and estimates of R0, eigenvalue ratio, and total contact 

```{r}
## library here package 
library(here)

## Load helper functions and library all packages used for analysis 
source(here("code", "helpers.R"))

## specify package options 
options(dplyr.summarise.inform = FALSE)

## set number of posterior predictive draws
num_draws <- 100

## set number of days to make predictions for (1 = April 11 2020)
days <- c(1:1)
```

```{r}
## read in reference data
acs_state_reference <- readRDS(here("data", "intermediate", "acs_state_reference.rds")) %>% 
  filter(agecat != "[0,18)") %>% 
  droplevels() %>% 
  select(hhsize, state, agecat, gender, race, prop, count) %>% 
  ungroup()

## read in acs state proportions 
acs_state_symmetry <- readRDS(here("data", "intermediate", "acs_state_symmetry.rds")) %>% 
  group_by(state) %>% 
  mutate(prop = count/sum(count)) %>% 
  ungroup() %>% 
  mutate(ego_age = agecat)

## national level symmetry
acs_national_symmetry <- readRDS(here("data", "intermediate", "acs_national_symmetry.rds")) 

## read in google mobility data 
google_pca_data <- read_rds(file=here('data', 'intermediate', 'google_mobility_pca.rds')) %>% 
  select(date, state = state, rolling_pca_3wks)

## Non-Household Model
nonhh_model <- read_rds(file = here('data', 'models', 'nonhh_model.rds'))

## Household Model 
hh_model <- read_rds(file = here('data', 'models', 'hh_model.rds'))
```


Create function for predictions 

```{r}
make_predictions <- function(day, nonhh_model = nonhh_model, hh_model = hh_model, draws = 100){

  ## read in acs data and format 
  acs_state_reference <- acs_state_reference %>% 
    mutate(hhsize_numeric = as.numeric(substring(hhsize, 1, 1))) %>% 
    mutate(day_std = day) %>% 
    mutate(date = as_date("2020-04-11") + day - 1) %>% 
    mutate(weekday = as.numeric(is_weekday(date))) %>% 
    left_join(google_pca_data, by = c("date", "state"))
  
  tic("predicted draws")
  
  ## Add predicted draws 
  predicted_draws <- acs_state_reference %>%
    add_predicted_draws(object = nonhh_model, ndraws = draws, allow_new_levels = T) %>% 
    mutate(numcc_predict = .prediction) %>% 
    ungroup() %>% 
    select(state, agecat, gender, hhsize, race, prop, weekday, count, day_std, .draw, numcc_predict, .category)

  ## Add predicted household draws
  predicted_draws_hh <- acs_state_reference %>%
    filter(hhsize != "1") %>% 
    add_predicted_draws(object = hh_model, ndraws = draws, allow_new_levels = T) %>% 
    mutate(numcc_predict_hh = .prediction) %>% 
    ungroup() %>% 
    select(state, agecat, gender, hhsize, race, prop, .draw, numcc_predict_hh, .category) %>% 
    mutate(.category = str_sub(.category, 1, str_length(.category)-2))

  toc()
  
  ## combine predicted draws 
  predicted_draws_total = predicted_draws %>% 
    left_join(predicted_draws_hh, by = c("state", "agecat", "gender", "hhsize", "race", ".draw", ".category")) %>% 
    mutate(numcc_predict_total = case_when(
      hhsize == "1" ~ numcc_predict,
      TRUE ~ numcc_predict + numcc_predict_hh
    ))
  
  ## summarize post-stratify estimates er
  state_level_predictions <- predicted_draws_total %>%
    group_by(state, .draw, .category, agecat) %>% 
    summarise(mean = sum(count/sum(count) * numcc_predict_total), warnings = F) %>% 
    mutate(day_std = day) %>%  
    ungroup()
  
  tic("enforce reciprocity")
  ## enforce reciprocity 
  state_level_predictions <- enforce_reciprocity(df = state_level_predictions)
  toc()

  tic("eigenvalue ratio")
  ## calculate eigenvalues, R0, q-index 
  eigenvalue_df <- eigenvalue_ratio(state_level_predictions)
  toc()
  
  ## calculate contact intervals 
  contact_df <- average_contact(state_level_predictions)

  ## add to list  
  newList <- list(eigenvalue_df, contact_df)
  
  ## write out and save predictions 
  # write_rds(x = newList, file = here('data', 'predictions', paste0('prediction_day', day, ".rds")))

  ## print out day to keep track 
  cat(day)
  
  ## return list with (1) summary statistics of contact (eigenvalue ratio, R0, q-index) 
  ## and (2) contact matrices (with credible intervals)
  return(newList)
}
```

## run functions 

```{r}
tic("total prediction time")
state_level_predictions_test <- map(days, ~make_predictions(.x, nonhh_model = nonhh_model, hh_model = hh_model, draws = num_draws))
toc()
```
