---
title: "Create Figures from our estimates"
author: Casey Breen
---

## Summary

This notebook contains code to produce all figures and tables for "Estimating Subnational Contact Patterns using Multilevel Regression with Poststratification." 

```{r}
## library package
library(here)

## helper functions and library packages
source(here("code", "helpers.R"))
```

## Read in data 

```{r}
## set working directory to read in draws
predictions <- list.files(path = here("data", "predictions_no_mobility"), pattern = ".rds", full.names = T) %>%
  map_dfr(read_rds)

## contact matrices predictions
contact_matrices_predictions <- predictions %>%
  bind_rows() %>%
  ungroup() %>%
  filter(is.na(.draw)) %>%
  mutate(date = as_date("2020-04-11") + day_std - 1) %>%
  mutate(month = floor_date(date, "months"))

## summary statistics predictions
summary_statistics <- predictions %>%
  bind_rows() %>%
  ungroup() %>%
  filter(!is.na(.draw)) %>%
  mutate(date = as_date("2020-04-11") + day_std - 1) %>%
  mutate(month = floor_date(date, "months")) %>%
  mutate(state = state)

## read in raw bics data 
df_formodel <- read_rds(here("data", "input", "bics_data_waves_1-6.rds"))

## top code total number of reported contacts at 30
top_code <- function(x) {
  x <- case_when(
    x > 30 ~ 30,
    TRUE ~ x
  )
}

## topcode data.frame
df_formodel_topcode <- df_formodel %>%
  mutate(across(c(starts_with("alter_age")), top_code)) %>%
  mutate(month = floor_date(as_date(startdate), "month"))

## read in acs data
acs_state_symmetry <- readRDS(here("data", "intermediate", "acs_state_symmetry.rds")) %>%
  group_by(state) %>%
  mutate(prop = count / sum(count)) %>%
  ungroup() %>%
  mutate(ego_age = agecat)

## q index 
google_pca_data <- read_rds(file = here("data", "intermediate", "google_mobility_pca.rds"))

```

# Replicate Figures 

Set-up: Calculate $R_0$ 

```{r}
## calculate R0
baseline_R0 <- 2.54

## baseline eigenvalue
polymod_country <- "United Kingdom"
polymod_age_limits <- c(0, 18, 25, 35, 45, 55, 65)

## get polynmod data
## supress warnings so it doesn't clog up pipeline
polymod_mat <- suppressMessages(suppressWarnings(getPolymodMatrixNoSchool(
  polymod_country = polymod_country,
  polymod_age_limits = polymod_age_limits
)))

prepandemic_eigenvalue <- eigen(polymod_mat)$values[1]

## calculate R0
summary_statistics <- summary_statistics %>%
  mutate(R0 = leading_eigenvalue / prepandemic_eigenvalue * baseline_R0) %>%
  mutate(eigenvalue_ratio = leading_eigenvalue / prepandemic_eigenvalue)
```

## Fig-1

Compare model-based predictions to raw survey results 

```{r}
## California raw estimates 
state_raw_estimates_ca <- df_formodel_topcode %>%
  filter(month <= as_date("2020-4-01")) %>%
  filter(state == "CA") %>%
  group_by(agecat, month) %>%
  summarise(across(starts_with("total_alter"), ~ mean(.x, na.rm = TRUE))) %>%
  pivot_longer(-c(agecat, month), names_to = "alter_age") %>%
  rename(mean = value) %>%
  mutate(alter_age = case_when(
    alter_age == "total_alter_age_0_18" ~ "[0,18)",
    alter_age == "total_alter_age_18_25" ~ "[18,25)",
    alter_age == "total_alter_age_25_35" ~ "[25,35)",
    alter_age == "total_alter_age_35_45" ~ "[35,45)",
    alter_age == "total_alter_age_45_55" ~ "[45,55)",
    alter_age == "total_alter_age_55_65" ~ "[55,65)",
    alter_age == "total_alter_age_65_100" ~ "[65,100]"
  )) %>%
  mutate(agecat = paste0("Ego Age: ", agecat)) %>%
  rename(.ego_age = agecat, .alter_age = alter_age)

## Alabama Raw Estimates 
state_raw_estimates_al <- df_formodel_topcode %>%
  filter(month <= as_date("2020-4-01")) %>%
  filter(state == "AL") %>%
  group_by(agecat, month) %>%
  summarise(across(starts_with("total_alter"), ~ mean(.x, na.rm = TRUE))) %>%
  pivot_longer(-c(agecat, month), names_to = "alter_age") %>%
  rename(mean = value) %>%
  mutate(alter_age = case_when(
    alter_age == "total_alter_age_0_18" ~ "[0,18)",
    alter_age == "total_alter_age_18_25" ~ "[18,25)",
    alter_age == "total_alter_age_25_35" ~ "[25,35)",
    alter_age == "total_alter_age_35_45" ~ "[35,45)",
    alter_age == "total_alter_age_45_55" ~ "[45,55)",
    alter_age == "total_alter_age_55_65" ~ "[55,65)",
    alter_age == "total_alter_age_65_100" ~ "[65,100]"
  )) %>%
  mutate(agecat = paste0("Ego Age: ", agecat)) %>%
  rename(.ego_age = agecat, .alter_age = alter_age)

ca_mrp <- contact_matrices_predictions %>%
  group_by(month, state, .ego_age, .alter_age) %>%
  summarize(
    sym_avg_per_ego = mean(contacts),
    lower = mean(lower),
    upper = mean(upper)
  ) %>%
  filter(state == "CA" & month <= as_date("2020-4-01")) %>%
  mutate(.ego_age = paste0("Ego Age: ", .ego_age)) %>%
  ggplot() +
  geom_pointrange(aes(
    x = forcats::fct_rev(.alter_age),
    ymin = lower,
    y = sym_avg_per_ego,
    ymax = upper,
    color = "MRP Estimate"
  )) +
  theme_half_open() +
  labs(
    x = "Alter Age",
    y = "Number of Contacts",
    title = paste0("California Predictions (April 2020, N = 95)")
  ) +
  geom_point(
    data = state_raw_estimates_ca %>% filter(month <= as_date("2020-4-01")),
    aes(
      x = forcats::fct_rev(.alter_age),
      y = mean,
      color = "BICS Data (Unadjusted)"
    ),
    size = 2.5
  ) +
  scale_color_manual(name = "", values = c("MRP Estimate" = "black", "BICS Data (Unadjusted)" = "red3")) +
  theme(legend.position = "none") +
  facet_grid(vars(month), vars(.ego_age)) +
  panel_border() +
  background_grid() +
  coord_flip() +
  ylim(0, 4)


## alabama plot 
al_mrp <- contact_matrices_predictions %>%
  group_by(month, state, .ego_age, .alter_age) %>%
  summarize(
    sym_avg_per_ego = mean(contacts),
    lower = mean(lower),
    upper = mean(upper)
  ) %>%
  ungroup() %>%
  filter(state == "AL" & month <= as_date("2020-4-01")) %>%
  mutate(.ego_age = paste0("Ego Age: ", .ego_age)) %>%
  ggplot() +
  geom_pointrange(aes(
    x = forcats::fct_rev(.alter_age),
    ymin = lower,
    y = sym_avg_per_ego,
    ymax = upper,
    color = "MRP Estimate"
  )) +
  theme_half_open() +
  labs(
    x = "Alter Age",
    y = "Number of Contacts",
    title = paste0("Alabama Predictions (April 2020, N = 9)")
  ) +
  geom_point(
    data = state_raw_estimates_al %>% filter(month <= as_date("2020-4-01")),
    aes(
      x = forcats::fct_rev(.alter_age),
      y = mean,
      color = "BICS Data (Unadjusted)"
    ),
    size = 2.5
  ) +
  scale_color_manual(name = "", values = c("MRP Estimate" = "black", "BICS Data (Unadjusted)" = "red3")) +
  theme(legend.position = "bottom") +
  facet_grid(vars(month), vars(.ego_age)) +
  panel_border() +
  background_grid() +
  coord_flip() +
  ylim(0, 4)

raw_vs_modeled_plot <- cowplot::plot_grid(ca_mrp, al_mrp, labels = "auto", nrow = 2)

ggsave(plot = raw_vs_modeled_plot, height = 12, width = 14, file = here("figures", "figures_no_mobility", "raw_vs_modeled_plot.png"))
```

## Fig-2: Contact Matrices

Plot contact matrix for each month 

```{r}
months <- contact_matrices_predictions %>%
  mutate(month = lubridate::format_ISO8601(month, precision = "ym")) %>%
  distinct(month) %>%
  pull()

for (month_i in months) {

  ## Example states: California, April 2020
  state_level_mixing_matrices_symmetrical <- contact_matrices_predictions %>%
    mutate(month = lubridate::format_ISO8601(month, precision = "ym")) %>%
    filter(month == month_i) %>%
    group_by(month, state, .ego_age, .alter_age) %>%
    summarize(
      sym_avg_per_ego = mean(contacts),
      lower = mean(lower),
      upper = mean(upper)
    ) %>%
    ggplot() +
    geom_tile(aes(x = .ego_age, y = .alter_age, fill = sym_avg_per_ego)) +
    # facet_grid(ego_sex ~ alter_sex) +
    coord_equal() +
    # viridis::scale_fill_viridis(name = str_wrap("Contacts per respondent", width = 10)) +
    scale_fill_gradientn(
      colors = viridis::viridis_pal()(9),
      limits = c(0, 4.41),
      na.value = "#FDE725FF",
      name = str_wrap("Contacts per respondent", width = 10)
    ) +
     facet_geo(~state) +
    theme_minimal(base_size = 9) +
    theme(
      axis.text.x = element_text(angle = 90),
      plot.title = element_text(size = 22),
      panel.spacing = unit(1, "lines")) + 
    labs(
      title = glue("State-Level Contact Matrices ({month_i})"),
      x = "Ego age",
      y = "Alter age"
    )

  ggsave(plot = state_level_mixing_matrices_symmetrical, height = 10, width = 13, file = here("figures", "figures_no_mobility", glue("state_level_mixing_matrices_symmetrical{month_i}.png")))
}
```

## Fig-3: Calculate eigenvalue ratio

Calculate eigenvalue ratio over time for all 50 states

```{r}
monthly_estimates_eigenvalue <- summary_statistics %>%
  group_by(date, state) %>%
  summarize(
    lower = quantile(eigenvalue_ratio, .1),
    upper = quantile(eigenvalue_ratio, .9),
    eigenvalue_ratio = mean(eigenvalue_ratio)
  ) %>%
  group_by(month = lubridate::floor_date(date, "month"), state) %>%
  summarize(
    lower = mean(lower),
    upper = mean(upper),
    eigenvalue_ratio = mean(eigenvalue_ratio)
  )

eigenvalue_plot_ribbon_month <- monthly_estimates_eigenvalue %>%
  ggplot(aes(x = month, y = eigenvalue_ratio, group = 1, ymin = lower, ymax = upper)) +
  geom_ribbon(fill = "grey80") +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 1, col = "black") +
  geom_vline(xintercept = as_date("2020-07-01"), linetype = "dashed", col = "grey25") +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  scale_y_continuous(breaks = c(0.2, 0.4, 0.6, 0.8, 1, 1.2, 1.4)) + 
  facet_geo(~state) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    x = "",
    y = "Relative Contact Intensity Index",
    title = ""
  ) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y") +
  theme(panel.spacing.x = unit(10, "mm"))

ggsave(plot = eigenvalue_plot_ribbon_month, height = 12, width = 18, file = here("figures", "figures_no_mobility", "eigenvalue_ratio_state_plot.png"))
```


## Appendix: Average Monthly Contacts 

Plot total average monthly total contacts (household and non-household) at the state level over time.  

```{r}
total_contact_predictions <- contact_matrices_predictions %>%
  mutate(ego_age = .ego_age) %>%
  left_join(acs_state_symmetry, by = c("state", "ego_age")) %>%
  group_by(state, date) %>%
  summarize(
    total_contact = sum(contacts * prop, na.rm = T),
    lower = sum(lower * prop, na.rm = T),
    upper = sum(upper * prop, na.rm = T)
  ) %>%
  ungroup() %>%
  mutate(weekday = is_weekday(lubridate::as_date(date) - 1)) %>%
  mutate(date = floor_date(as_date(date), "month")) %>%
  group_by(state, date) %>%
  summarize(
    total_contact = mean(total_contact),
    lower = mean(lower),
    upper = mean(upper)
  )

total_contacts_plot <- total_contact_predictions %>%
  ungroup() %>%
  ggplot(aes(x = date, y = total_contact, ymin = lower, ymax = upper, group = 1)) + #
  geom_ribbon(fill = "grey80") +
  geom_point() +
  geom_line() +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  ggsci::scale_color_lancet() +
  facet_geo(~state) +
  labs(
    x = "Date",
    y = "Total Contact",
    title = ""
  ) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y") +
  theme(panel.spacing.x = unit(10, "mm"))

ggsave(plot = total_contacts_plot, height = 12, width = 18, file = here("figures", "figures_no_mobility", "total_contact_state_plot.png"))
```



## Appnedix: R0 over time 

```{r}
monthly_estimates_R0 <- summary_statistics %>%
  group_by(date, state) %>%
  summarize(
    lower = quantile(R0, .1),
    upper = quantile(R0, .9),
    R0 = mean(R0)
  ) %>%
  group_by(month = lubridate::floor_date(date, "month"), state) %>%
  summarize(
    lower = mean(lower),
    upper = mean(upper),
    R0 = mean(R0)
  )

R0_plot_ribbon_month <- monthly_estimates_R0 %>%
  ggplot(aes(x = month, y = R0, group = 1, ymin = lower, ymax = upper)) +
  geom_ribbon(fill = "grey80") +
  geom_point() +
  geom_line() +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  facet_geo(~state) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    x = "Date",
    y = "R0",
    title = ""
  ) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y") +
  theme(panel.spacing.x = unit(10, "mm"))

ggsave(plot = R0_plot_ribbon_month, height = 12, width = 18, file = here("figures", "figures_no_mobility", "R0_state_plot.png"))
```

## Fig-4: Reproductive Values

Calculate relative reproductive values. This is equivalent to the left eigenvector. 

```{r}
## select states and calculate standardized eigenvectors 
left_eigenvector <- summary_statistics %>%
  filter(state %in% c("CA", "NY", "TX")) %>%
  select(state, day_std, .draw, left_eigenvector) %>%
  unnest(left_eigenvector) %>%
  group_by(state, day_std, .draw) %>%
  mutate(left_eigenvector_standardized = abs(eigenvector / first(eigenvector))) %>%
  ungroup()

## calculate mean and 80% credible interval of relative reproductive values 
example_state_left <- left_eigenvector %>%
  mutate(date = as_date("2020-04-11") + day_std) %>%
  mutate(month = lubridate::floor_date(date, "month")) %>%
  filter(month %in% c(as_date(" 2020-04-01"), as_date("2021-1-01"), as_date("2021-5-01"))) %>%
  group_by(state, agecat, month) %>%
  summarize(
    left_eigenvector_mean = mean(left_eigenvector_standardized),
    lower = quantile(left_eigenvector_standardized, 0.1),
    upper = quantile(left_eigenvector_standardized, 0.9)
  ) 

## plot reproductive numbers 
reproductive_values <- example_state_left %>%
  ggplot(aes(
    x = agecat,
    y = left_eigenvector_mean,
    fill = state,
    ymin = lower,
    ymax = upper
  )) +
  geom_col(position = "dodge", width = .75, size = 3) +
  geom_linerange(position = position_dodge(.75)) +
  theme_cowplot() +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = "bottom") +
  labs(
    x = "Age Group",
    y = ""
  ) +
  facet_wrap(~ as_date(month))

## save relative reproductive values plot 
ggsave(plot = reproductive_values, height = 7, width = 17, file = here("figures", "figures_no_mobility", "reproductive_values_plot.png"))
```

## Appendix: Q index plot 

Calculate q-index plots showing assortativity with respect to age. 

```{r}
## calculate q index 
## q-index is absolute value of ratio of second eigenvector to first eigenvector
q0_data <- summary_statistics %>%
  group_by(date, state) %>%
  summarize(
    lower = quantile(R0, .1),
    upper = quantile(R0, .9),
    R0 = mean(abs(R0)),
    leading_eigenvalue = mean(leading_eigenvalue),
    lower_q0 = quantile(abs(q_index), .1),
    upper_q0 = quantile(abs(q_index), .9),
    q0 = mean(abs(q_index))
  ) %>%
  group_by(month = lubridate::floor_date(date, "month"), state) %>%
  summarize(
    lower = mean(lower),
    upper = mean(upper),
    R0 = mean(R0),
    leading_eigenvalue = mean(leading_eigenvalue),
    lower_q0 = quantile(abs(lower_q0), .1),
    upper_q0 = quantile(abs(upper_q0), .9),
    q0 = mean(q0)
  )

## plot how q index changed over time 
q_index_over_time <- q0_data %>%
  group_by(month) %>%
  summarize(q_index = mean(q0)) %>%
  ggplot(aes(x = month, y = q_index)) +
  geom_point() +
  theme_cowplot() +
  labs(
    title = "Q-index Over Time (State Average)",
    y = "q-index"
  )

## plot association between q-index 
q_index_association_R0 <- q0_data %>%
  group_by(month) %>%
  summarize(
    q_index = mean(q0),
    q_index_lower = mean(lower_q0),
    q_index_upper = mean(upper_q0),
    R0 = mean(R0)
  ) %>%
  ggplot(aes(x = q_index, y = R0)) +
  geom_point() +
  theme_cowplot() +
  labs(
    title = "Association between R0 and Q-index (State Average)",
    y = "R0"
  )

q_index_plots <- cowplot::plot_grid(q_index_over_time, q_index_association_R0, labels = "auto")


ggsave(plot = q_index_plots, height = 7, width = 14, file = here("figures", "figures_no_mobility", "q_index_plot.png"))
```

## CA mobility and predictions plot 

```{r}
eigenvalue_df <- summary_statistics %>%
  mutate(eigenvalue_ratio = leading_eigenvalue / prepandemic_eigenvalue) %>%
  group_by(state, day_std) %>%
  summarize(
    lower = quantile(eigenvalue_ratio, .1),
    upper = quantile(eigenvalue_ratio, .9),
    eigenvalue_ratio = mean(eigenvalue_ratio)
  )

ca_plot <- eigenvalue_df %>%
  filter(state == "CA") %>%
  mutate(date = as_date("2020-04-11") + day_std - 1) %>%
  mutate(weekday = case_when(
    as.numeric(is_weekday(date)) == 1 ~ "weekday",
    TRUE ~ "weekend"
  )) %>%
  ggplot(aes(x = date, y = eigenvalue_ratio, group = 1, ymin = lower, ymax = upper)) +
  geom_ribbon(fill = "grey80") +
  geom_point(aes(color = weekday)) +
  #  geom_hline(yintercept = 1, linetype = "dashed", col = "black") +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  ggsci::scale_color_lancet() +
  labs(
    x = "=",
    y = "Contact Intensity Index",
    title = "Daily Predictions"
  ) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y")


pc1_plot <- google_pca_data %>%
  mutate(holidays = case_when(
    date == as_date("2020-09-07") ~ "Labor Day",
    date == as_date("2020-11-26") ~ "Thanksgiving",
    date == as_date("2020-12-25") ~ "Christmas Day",
    date == as_date("2021-01-01") ~ "New Years Day",
    TRUE ~ NA_character_
  )) %>%
  filter(state == "CA" & date >= as_date("2020-04-11") & date <= as_date("2021-05-26")) %>%
  group_by(month = as_date(date)) %>%
  ggplot(aes(x = month, y = -PC1)) +
  geom_point() +
  # geom_line() +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  gghighlight(!is.na(holidays), label_key = holidays) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    x = "Date",
    y = "PC1",
    title = "Mobility PC1: Daily"
  ) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y") +
  ylim(-8, 0.5)

pc1_rolling_plot <- google_pca_data %>%
  filter(state == "CA" & date >= as_date("2020-04-11") & date <= as_date("2021-05-26")) %>%
  ggplot(aes(x = date, y = -rolling_pca_3wks)) +
  geom_point() +
  # geom_line() +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    x = "Date",
    y = "PC1",
    title = "Mobility PC1: Three-Week Rolling Average"
  ) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y") +
  ylim(-8, 0.5)

raw_reported_contact <- df_formodel_topcode %>%
  mutate(state == "CA") %>%
  group_by(month = lubridate::floor_date(as_date(startdate), "month")) %>%
  summarise(raw_contact = mean(alter_age_0_18 + alter_age_18_25 + alter_age_25_35 + alter_age_35_45 +
    alter_age_45_55 + alter_age_55_65 + alter_age_65_100)) %>%
  ggplot(aes(x = month, y = raw_contact)) +
  geom_point() +
  geom_line() +
  theme_cowplot() +
  panel_border() +
  ylim(0, 6) +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    x = "Date",
    y = "Non-HH Contacts",
    title = "Monthly Avg. Reported Contact (BICS; unadjusted)"
  ) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y")


## R0 ribbon CA
R0_plot_ribbon_month_ca <- monthly_estimates_R0 %>%
  filter(state == "CA") %>%
  ggplot(aes(x = month, y = R0, group = 1, ymin = lower, ymax = upper)) +
  geom_ribbon(fill = "grey80") +
  geom_point() +
  geom_line() +
  theme_cowplot() +
  panel_border() +
  background_grid() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    x = "Date",
    y = "R0",
    title = "Change in R0 Over Time"
  ) +
  scale_x_date(date_breaks = "2 month", date_labels = "%b-%Y") +
  theme(panel.spacing.x = unit(10, "mm"))

## plot grid
bottom_row <- plot_grid(pc1_plot, pc1_rolling_plot, labels = c("a", "b"))
mid_row <- plot_grid(raw_reported_contact, R0_plot_ribbon_month_ca, labels = c("c", "d"))

ca_plot <- cowplot::plot_grid(bottom_row, mid_row, ca_plot, labels = c("", "", "e"), ncol = 1)

ggsave(plot = ca_plot, height = 18, width = 14, file = here("figures", "figures_no_mobility", "ca_plot.png"))
```

## Tables and numbers reported in text 

Table 1: number of interviews conducted per month 

```{r}
df_formodel %>% 
  count(month)
```

Table 2: model selection (run `06_model_selection_loo.Rmd`)

Numbers reported in text: Iowa vs. Washington change in contact intensity over time (page 14)

```{r}
## monthly estimates eigenvalue 
monthly_estimates_eigenvalue %>%
  filter(state %in% c("IA", "WA")) %>%
  filter(month %in% c(as_date("2021-05-01"), as_date("2020-04-01	"))) %>% 
  select(month, state, eigenvalue_ratio) %>% 
  pivot_wider(names_from = state, values_from = eigenvalue_ratio) %>% 
  mutate(diff = ((IA / WA)-1)*100)
```


